### 2015-09-29 untitled.tex
edited untitled.tex

With the above discussions, for the most simple case defined above, the problem is basically identical to the worst-case response time analysis of segmented self-suspending task systems. It has been recently shown by Nelissen et al. \cite{ecrts15nelissen} that calculating the worst-case response time of such a problem is a challenging problem. Nelissen et al. \cite{ecrts15nelissen} explain misconceptions conducted by using wrong assumptions in the critical instant theorem. However, their approaches require exponential time complexity to derive $W_k^{j}$.

>>>>

With the above discussions, for the most simple case defined above, the problem is basically identical to the worst-case response time analysis of segmented self-suspending task systems. It has been recently shown by Nelissen et al. \cite{ecrts15nelissen}  calculating the worst-case response time in the above case is already a very challenging problem. Nelissen et al. \cite{ecrts15nelissen} identify several misconceptions used in the literature for this problem. After excluding those misconceptions, deriving the worst-case response time of a computation segment in pseudo-polynomial time seems to be a very difficult problem. Due to \cite{ecrts15nelissen}, the only existing solution to derive the exact $W_k^{j}$ requires exponential time complexity.
